
---
title: "MuSu_(NA, c, NA)"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
suppressMessages(library(pander))
suppressMessages(library(psych))
suppressMessages(library(DistatisR))
suppressMessages(library(tidyr))
suppressMessages(library(magrittr))
suppressMessages(library(DistatisR))
suppressMessages(library(PTCA4CATA))
suppressMessages(library(ExPosition))
suppressMessages(library(InPosition))
suppressMessages(library(superheat))
suppressMessages(library(gridExtra))
suppressMessages(library(ggplotify))
suppressMessages(library(grid))
suppressMessages(library(pals))
```

> This is an SVD with centered columns.

##### Data:

###### The data are from the morning scan club (MSC) resting-state data where each of the 10 participants were scanned 10 times. The data that are analyzed here are the z-transformed coefficients of correlation between regions. These regions can be categorized into 12 networks: 

```{r community_list, echo = FALSE, fig.height= 10, fig.width = 2}
# rename communities
#--- read the file with community information: label number & community name & color & abbreviation for community name
parcel.comm.path <- "data/parcel_community"
CommName <- read.csv("../data/parcel_community/systemlabel.txt",header = FALSE)
colnames(CommName) <- c("Comm", "CommLabel","CommColor","CommLabel.short")
CommName[,'Community'] <- c("UnAssign", "Default","lateral Visual","Frontoparietal",
                            "medial Visual","dorsal Attention","Premotor",
                            "ventral Attention","Salience","Cingular opercular",
                            "Sensorimotor - hand","Sensorimotor - face","Auditory",
                            "anterior Medial temporal","posterior Medial temporal",
                            "Parietal memory","Context","Sensorimotor - foot","Unknown")
pander::pander(CommName[,c("Comm", "Community","CommLabel.short")])

```

###### As a result, the correlation matrix of each session of each subject will look like this:

```{r data, echo = FALSE, include = TRUE, fig.height= 20, fig.width = 16}
zmat.path <- "../data/zmat"
load(paste0(zmat.path,"/sub-MSC01_zcube_rcube.RData"))
# read parcel labels
parcel.comm.path <- "../data/parcel_community"
vox.des <- read.table(paste0(parcel.comm.path,"/sub-MSC01_node_parcel_comm.txt"),sep = ",")
colnames(vox.des) <- c("NodeID","VertexID","Comm")
#--- create three columns in the original table of community information: name, color, abbreviation
for(i in 1:nrow(CommName)){
  vox.des$Comm.recode[vox.des$Comm==CommName$Comm[i]] <- as.character(CommName$CommLabel[i])
  vox.des$Comm.Col[vox.des$Comm==CommName$Comm[i]] <- as.character(CommName$CommColor[i])
  vox.des$Comm.rcd[vox.des$Comm==CommName$Comm[i]] <- as.character(CommName$CommLabel.short[i])
}
#--- Create design matrix for communities
vox.des.mat <- makeNominalData(as.matrix(vox.des$Comm.rcd))
colnames(vox.des.mat) <- sub(".","",colnames(vox.des.mat))

#--- Create color for each communities
Comm.col <- list(oc = as.matrix(vox.des$Comm.Col), gc = as.matrix(CommName$CommColor))
rownames(Comm.col$oc) <- vox.des$NodeID
rownames(Comm.col$gc) <- CommName$CommLabel.short

superheat(cubes$rcube[,,1],
          membership.cols = vox.des$Comm.rcd,
          membership.rows = vox.des$Comm.rcd,
          clustering.method = NULL,
          heat.col.scheme = "viridis",
          left.label.size = 0.08,
          bottom.label.size = 0.05,
          y.axis.reverse = TRUE,
          left.label.col = Comm.col$gc[order(rownames(Comm.col$gc))], # order by community name
          bottom.label.col = Comm.col$gc[order(rownames(Comm.col$gc))],
          left.label.text.size = c(rep(6,4), rep(3,3),6,3,  rep(6,2),3,rep(6,5),3,3),
          bottom.label.text.size = 2,
          left.label.text.col = c(rep("black",8),rep("white",2),rep("black",3),"white",rep("black",3),rep("white",2)),
          bottom.label.text.col = c(rep("black",8),rep("white",2),rep("black",3),"white",rep("black",3),rep("white",2)),
          left.label.text.alignment = "left",
          title = "Correlation matric of the 1st session of Subject 1"
)
```

###### This correlation matrix were then turned into a rectangular matrix

#### Rectangular data:

+ Rows: 5 sessions

+ Columns: Different edges (e.g, _within DMN_, _between DMN & CON_, _between DMN & FPN_, etc.) of different subjects

_Note: The data was transformed from the upper triangle of the correlation matrices. From the correlation matrix of each session, its upper triangle are reshape as a vector. These sessions are concatenated on the rows and these of different subjects are concatenated on the columns._

### The grand table:
```{r gt_heatmap, echo = FALSE, fig.height= 8, fig.width = 16}
# the labels for each intersection of the correlation matirx
load(paste0("../data/grandatble_and_labels_20190204.Rdata")) # read the labels of grandtable
# Categorize columns by between or within edges
#--- Create new column of sub-edgetype
sprintf('%s_%s',labels$subjects_label,labels$wb)
labels[,'subjects_wb'] <- sprintf('%s_%s',labels$subjects_label,labels$wb)
#--- Heatmap of the grand table
superheat(gt,
          membership.cols = labels$subjects_edge_label,
          membership.rows = c(1:10),
          clustering.method = NULL,
          heat.col.scheme = "viridis",
          left.label.size = 0.05,
          bottom.label.size = 0.05,
          y.axis.reverse = TRUE,
          left.label.text.size = 3,
          bottom.label.text.size = 2,
          left.label.text.alignment = "left",
          grid.vline = FALSE
)
```

##### Method:

+ Centering: across sessions (rows) (i.e., the columns are centered)

+ Normalizing: none

